INGRID: Creating Languages in MPS from ANTLR Grammars

### 2016-10-29 chapters/language_definition.tex
textgen - in progress

@@

The final/last, fourth step, is to create the TextGen aspect for each AST node.
The purpose of the TextGen aspect is to define, for a language element (AST node), what code in the BaseLanguage will be generated out of it, once we want to compile and run our MPS code/program.
This is needed to allow/enable users to generate plain-text source code representation out of the AST they built/created inside MPS.
Again, a TextGen aspect must be created for each language element.
Basically, it is a single method in the BaseLanguage (or in Java?) for each language element.
The method generates a string (plain-text) representation of the element, appends the string to the output stream, and then calls TextGen methods on all children of the element.

A very basic example of BaseLanguage code that can be used as the TextGen aspect of an \mpsconcept{Element{\_}1} node, which represents the full XML tag with content, is shown in Figure~\ref{fig:textgen_example}.
It appends all literals, properties, and children in the same order as they appear in the grammar definition.

\begin{figure}[ht]
	\centering
	\includegraphics[width=90mm]{./images/textgen_example.png}
	\caption{Example of a~TextGen aspect}
	\label{fig:textgen_example}
\end{figure}

>>>>

The purpose of the last phase of the MPS language construction is to generate the TextGen aspect for each concept.
We use the \mpsconcept{Element{\_}1} concept again for illustration.
Figure~\ref{fig:TEXTGENEX} shows a very basic example of BaseLanguage code that can be used as its TextGen aspect.
The code appends all literals, properties, and children of \mpsconcept{Element{\_}1} to the output buffer, and does that in the same order as they appear in the corresponding grammar rule.

\begin{figure}[ht]
\begin{alltt}
\small
\mpstgkeyword{text gen component for concept} \mpstgtarget{Element{\_}1} \{
  \mpstgparam{(context, buffer, node)->void} \{
    \mpstgaction{append} \{\mpstgliteral{<}\};
    \mpstgaction{append} \$\{\mpstgparam{node}.\mpstgnodeprop{\textit{Name}}{\_}\textit{1}\};
    \mpstgaction{append} \{\ \};
    \mpstgaction{append} \$list\{\mpstgparam{node}.\mpstgnodeprop{\textit{Attribute}}{\_}\textit{1}\};
    \mpstgaction{append} \{\mpstgliteral{>}\};
    \mpstgaction{append} \$list\{\mpstgparam{node}.\mpstgnodeprop{\textit{Content}}{\_}\textit{2}\};
    \mpstgaction{append} \{\mpstgliteral{</}\};
    \mpstgaction{append} \$\{\mpstgparam{node}.\mpstgnodeprop{\textit{Name}}{\_}\textit{2}\};
    \mpstgaction{append} \{\mpstgliteral{>}\};
  \}
\}
\end{alltt}
\caption{Basic TextGen aspect for the \mpsconcept{Element{\_}1} concept}
\label{fig:TEXTGENEX}
\end{figure}

@@
